A Responsible Machine Learning Workflow\\\normalsize{With Focus on Interpretable Models, Post-hoc Explanation, and Discrimination Testing}

### 2020-02-02 article-information-2019.tex
a perhaps not broken structure that adheres to the suggested 16-page limit

Tables \ref{tab:mort_disc}\textbf{a} and \ref{tab:mort_disc}\textbf{b} show the results of the discrimination tests using the mortgage data for two sets of class-control groups: blacks as compared to whites, and females as compared to males. As with the simulated data in Table \ref{tab:sim_disc}, several measures of disparities are shown, with the SMDs calculated using the probabilities from $g^{\text{MGBM}}$ and $g^{\text{XNN}}$, and the accuracy, false positive rates (FPRs), and  FPR ratios, MEs, and AIRs calculated using a binary outcome based on a cutoff of 0.20 (anyone with probabilities of 0.2 or less receives the favorable outcome).\footnote{See Appendix \ref{a_sec:cut} for comments pertaining to cutoff selection and discrimination testing.} Since $g^{\text{MGBM}}$ and $g^{\text{XNN}}$  are predicting the likelihood of receiving a high-priced loan, $g^{\text{MGBM}}$ and $g^{\text{XNN}}$ assume that a lower score is favorable.  Thus, one might consider FPR ratios as a measure of the class-control disparities. FPR ratios are higher under $g^{\text{XNN}}$ than $g^{\text{MGBM}}$ (2.45 vs. 2.10) in Table \ref{tab:mort_disc}\textbf{b}, but overall FPRs are lower for blacks under $g^{\text{XNN}}$ (0.295 vs. 0.315) in Table \ref{tab:mort_disc}\textbf{a}.  This is the same pattern seen in the simulated data results in Section \ref{ssec:dis_sim}, again leading to the question of whether a fairness goal should not only consider class-control relative rates, but also intra-class improvements in the chosen fairness metric.  Similar results are found for the female-male comparison, but the relative rates are less stark: 1.15 for $g^{\text{MGBM}}$ and 1.21 for $g^{\text{XNN}}$.

>>>>

Tables \ref{tab:mort_disc}\textbf{a} and \ref{tab:mort_disc}\textbf{b} show the results of the discrimination tests using the mortgage data for two sets of class-control groups: blacks as compared to whites, and females as compared to males. As with the simulated data in Table \ref{tab:sim_disc}, several measures of disparities are shown, with the SMDs calculated using the probabilities from $g^{\text{MGBM}}$ and $g^{\text{XNN}}$, and the accuracy, false positive rates (FPRs), and  FPR ratios, MEs, and AIRs calculated using a binary outcome based on a cutoff of 0.20 (anyone with probabilities of 0.2 or less receives the favorable outcome).\footnote{See Appendix \ref{a_sec:cut} for comments pertaining to cutoff selection and discrimination testing.} Since $g^{\text{MGBM}}$ and $g^{\text{XNN}}$  are predicting the likelihood of receiving a high-priced loan, $g^{\text{MGBM}}$ and $g^{\text{XNN}}$ assume that a lower score is favorable.  Thus, one might consider FPR ratios as a measure of the class-control disparities. FPR ratios are higher under $g^{\text{XNN}}$ than $g^{\text{MGBM}}$ (2.45 vs. 2.10) in Table \ref{tab:mort_disc}\textbf{b}, but overall FPRs are lower for blacks under $g^{\text{XNN}}$ (0.295 vs. 0.315) in Table \ref{tab:mort_disc}\textbf{a}.  This is the same pattern seen in the simulated data results in Section \ref{ssec:dis_sim}, again leading to the question of whether a fairness goal should not only consider class-control relative rates, but also intra-class improvements in the chosen fairness metric.  Similar results are found for the female-male comparison, buat the relative rates are less stark: 1.15 for $g^{\text{MGBM}}$ and 1.21 for $g^{\text{XNN}}$.
